%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Atul}{Chaudhary}{
\href{mailto:chaudharyatul444@gmail.com}{chaudharyatul444@gmail.com} | +91 9756516904
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Meerut Institute of}
\subsection{Engg \& Technology}
\descript{B.Tech in Computer Science}
\location{2016 - 2020 | CGPA 8.4}
\sectionsep

\subsection{J.P Academy}
\descript{Sr. Secondary (12th)}
\location{2015 - 2016 | Meerut, UP, India}
\location{ Cum. Per: 85.2\%}
\sectionsep

\subsection{J.P Academy}
\descript{Secondary School (10th)}
\location{2013 - 2014 | Meerut, UP, India}
\location{ CGPA : 8.4 }
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Proficient:}
\textbullet{}Java \\
\textbullet{} Spring-boot \\
\textbullet{} Micro-Services \\
\textbullet{} Rest API's \\
\textbullet{} jenkins \\
\textbullet{}  MongoDB \\
\textbullet{}  Amazon Web Services \\
\location{Familiar:}
\textbullet{} Python \\
\textbullet{} HTML \\
\textbullet{} CSS \\
\textbullet{} React \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Leetcode:// \href{https://leetcode.com/atul-chaudhary/}{\bf atul-chaudhary} \\
Github:// \href{https://github.com/atul-chaudhary}{\bf atul-chaudhary} \\
StackOverflow://  \href{https://stackoverflow.com/users/8145335/atul-chaudhary}{\bf atul-chaudhary} \\
LinkedIn://  \href{https://www.linkedin.com/in/atul-chaudhary/}{\bf atul-chaudhary} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Data Structures and Algorithms  \\
Object Oriented Programming \\
Operating Systems \\
Database Management System \\
Computer Networks \\
Cloud Computing \\

\sectionsep

\subsection{Training}
\location{Infosys}
Java-Angular FullStack Training \\
\location{Geeks For Geeks}
Data Structures and Algorithms \\


\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Infosys}
\descript{| Specialist Programmer (SDE 1) }
\location{Jan 2022 - Present | Hyderabad, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Spearheaded the development and maintenance of a new
micro-service for Exception-Mapping from scratch, enabling
Store Planner to perform efficient inventory mappings from
the distribution centres to Active GAP stores.
\item Implemented streamlined bulk updates in the SPM service by
designing and constructing efficient logic, reducing total
processing time by 50%.
\item Contributed to the optimization and bug-fixing efforts of
the New-Store Management Service while also developing
and integrating various new endpoints to enhance its
functionality.
\end{tightemize}
\sectionsep

\runsubsection{Infosys}
\descript{| Digital Specialist Engineer }
\location{Nov 2020 - Jan 2022 | Hyderabad, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Maintained critical backend services for SPM and New-Store, ensuring they meet the high standards and requirements of
Store Planners and the client.
\item Developed new endpoints and increased test coverage by
15\% for both JUnit and Integration test cases in SPM and NS.
\end{tightemize}
\sectionsep


\runsubsection{Rootsapp}
\descript{| Software Developer Intern }
\location{Jun 2018 – Dec 2018 | Meerut, UP, India}
\begin{tightemize}
\item Built a Smart Student Attendance System using AWS Rekognition Kit, allowing attendance to be taken for an entire class with a single photo click.
\item Designed and developed the Android application module and AWS Lambda function, playing a major role in the system's development.
\item Utilized a tech stack consisting of Java, Android, AWS Lambda, AWS API Gateway, and AWS RDS to develop the system.

\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROJECTS}
\runsubsection{Denphy - Wallpaper App}
\descript{| \href{https://github.com/atul-chaudhary/flutter_wallpaper_app/}{\bf Link}}
\begin{tightemize}
\item Developed a high-quality Wallpaper Application using Flutter, and uses Firebase for backend and storing the wallpapers.
\item Designed to simplify the process of finding and setting wallpapers and backgrounds on both home and lock screens, allowing users to easily access and use images from a variety of genres.

\end{tightemize}
\sectionsep

\runsubsection{R.E.D-Blood Donation App}
\descript{| \href{https://github.com/atul-chaudhary/R.E.D-BloodDonationApp}{\bf Link}}
\begin{tightemize}
\item Developed the RED-Blood Donation App as part of the Smart
MIET Hackathon at the college level, with the aim of creating a
reliable platform connecting blood donors and those in need.
\item Implemented a user-friendly interface that enables donors to
easily view nearby donation requests, while allowing those in
need to quickly request assistance from donors in their area.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{ACHIEVEMENTS}
\textbullet{} Solved 500+ DSA questions on Leetcode and GeekforGeeks.  \\
\textbullet{} Mentored new GAP joiners as part of the Store Planning Team. \\
\textbullet{} Placed third in the Smart MIET Hackathon by developing a blood
donation app in just 24 hours.

\end{minipage}
\end{document}  \documentclass[]{article}
